\input{../common/preamble.tex}   % your formatting setup
\begin{document}

\input{../common/header.tex}        % include your header

% Sections
% --- Summary ---
\section*{Summary}
Data Engineer with 2.2 years of experience building scalable data pipelines and backend systems. Skilled in Python, SQL, AWS, and Snowflake, with proven success in automating deployments and cutting manual effort. Strong communicator, recognized with multiple awards for innovation, quality, and high-impact delivery.
\section*{Skills}
\begin{itemize}[leftmargin=0.5cm, label={}]
    \item \textbf{Programming Languages:} Python, SQL
    \item \textbf{Data Engineering Tools:} Apache Airflow, UC4, Snowflake
    \item \textbf{Frameworks:} Django, Streamlit
    \item \textbf{Databases:} MySQL, PostgreSQL
    \item \textbf{Cloud Platforms \& DevOps:} AWS, GCP, Git, Docker, Kubernetes
\end{itemize}

\section*{Certifications}
\input{../common/certifications.tex}   

% --- Experience ---
\section*{Experience \hfill \textit{Factspan Analytics, Bangalore}}

\textbf{Senior Analyst (Data Engineering / Data Science role)} \hfill Jan 2026 – Present
\vspace{0.2cm}
\hrule
\vspace{0.2cm}

\begin{itemize}[leftmargin=0.5cm]
\item \textbf{Entertainment Industry Leadership:} Spearheaded the design and implementation of dbt models within a fully automated, scalable data pipeline for a Fortune 500 global entertainment leader. Optimized data architecture to support high-concurrency reporting and real-time analytics.
\item \textbf{Engineering Automation:} Engineered a custom automation framework to generate dbt models directly from client requirements; reduced manual development effort by 50\% and minimized human error in the ETL lifecycle.
\item \textbf{GenAI Infrastructure:} Led the data engineering workstream for a Generative AI application for a premier global insurance provider, focusing on high-performance vector data ingestion and pipeline reliability.
\item \textbf{Cross-Functional Strategy:} Orchestrated the data engineering roadmap and collaborated on data science modeling for a major fashion marketing firm, successfully delivering their inaugural data science initiative.
\item \textbf{Recognitions:} Received the \textit{``Deliver the Results''} award for consistently exceeding performance benchmarks and project milestones.
\end{itemize}

\vspace{0.2cm}
\textbf{Analyst (Data Engineering)} \hfill Jan 2024 – Jan 2026
\vspace{0.1cm}
\hrule
\vspace{0.2cm}

\begin{itemize}[leftmargin=0.5cm]
\item \textbf{Scalable Data Ingestion:} Designed and maintained ETL pipelines using \textbf{Python, Airflow, and AWS} for a global entertainment client, managing the ingestion of multi-terabyte datasets from fragmented sources into \textbf{Snowflake}.
\item \textbf{Legacy Modernization:} Executed the migration of legacy on-premise data warehouses to Snowflake, implementing clustering and performance tuning that significantly boosted query throughput.
\item \textbf{Data Governance \& Quality:} Developed automated data quality frameworks and unit testing workflows, ensuring high data integrity and reducing manual validation effort by 50\%.
\item \textbf{DevOps Integration:} Utilized enterprise-level platform architecture to enable \textbf{CI/CD workflows}, streamlining deployment cycles and improving the reliability of data engineering operations.
\item \textbf{Recognitions:} Awarded \textit{Learning Champ''} for training excellence, \textit{Sweat the Details''} for quality-driven innovation, and a \textit{``Spot Award''} for critical project contributions.
\end{itemize}

% --- Projects ---
\section*{Projects}
\vspace{0.3cm}

\noindent \textbf{2 x High-Velocity Data Ingestion} \hfill \textit{AWS DMS, Snowflake, Java, APIs}
\hrule
\begin{itemize}[leftmargin=0.5cm, nosep]
    \item Spearheaded the migration of legacy warehouses to \textbf{Snowflake} using a \textbf{Medallion Architecture} to ensure structured data governance and analytical readiness.
    \item Integrated diverse data streams including MySQL and real-time \textbf{API streaming} into a unified Snowflake ecosystem.
    \item Implemented robust DBT ETL worflows and validation frameworks to ensure data quality and reliability across the ingestion pipeline.
    \item Developed a specialized \textbf{Java application} for the to handle serial number mapping and complex data reconciliation.
\end{itemize}

\vspace{0.3cm}

\noindent \textbf{Enterprise GenAI Discovery Chatbot} \hfill \textit{Snowflake, OpenAI, Python, Streamlit}
\hrule  
\begin{itemize}[leftmargin=0.5cm, nosep]
    \item Developed a \textbf{Snowflake-native LLM application} allowing stakeholders to query data warehouse metadata using natural language, reducing ad-hoc discovery requests by 30\%.
    \item Architecting a transition to a standalone \textbf{Claude/Anthropic} integration to leverage enterprise-grade security and expanded context windows for complex schema interpretation.
\end{itemize}

\vspace{0.3cm}

\noindent \textbf{LLM-Powered Automated Report Validation} \hfill \textit{Python, LangChain, OpenAI, SQL}
\hrule
\begin{itemize}[leftmargin=0.5cm, nosep]
    \item Engineered an automated parity-testing engine to validate data integrity between legacy systems and newly generated \textbf{Catalyst} reports for a global insurance leader.
    \item Implemented semantic matching logic to identify discrepancies in unstructured fields, ensuring 100\% data accuracy during a critical platform migration.
\end{itemize}

\vspace{0.3cm}

\noindent \textbf{Industrial-Scale ETL Modernization} \hfill \textit{Python, Pandas, SQL}
\hrule
\begin{itemize}[leftmargin=0.5cm, nosep]
    \item Orchestrated the refactoring of \textbf{400+ legacy .sas workflows} into modular, maintainable Python scripts, eliminating high-cost proprietary licensing and improving processing speeds.
    \item Standardized cross-project data logic by implementing reusable Python decorators and robust logging frameworks for error handling.
\end{itemize}

% --- Education ---
\input{../common/education.tex}     % include your education section

% --- Publications ---
\input{../common/publications.tex}   % include your publications section

\end{document}