\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem} % for clean bullet points
\usepackage[hidelinks]{hyperref} % clickable links without colors
\setlist[itemize]{noitemsep, topsep=0pt} % compact lists

% --- Header ---
\begin{document}
\begin{center}
    {\LARGE \textbf{Shyam Mohan V M}} \\[4pt]
    {\normalsize \textbf{Data Engineer}} \\[6pt]
    Bangalore, India \textbar{} 
\href{mailto:shyammohanvm@gmail.com}{shyammohanvm@gmail.com} \textbar{} 
+91-7034830977 \textbar{} 
\href{https://www.linkedin.com/in/shyammohanvm/}{linkedin.com/in/shyammohanvm}
\end{center}
\hrule
\vspace{0.5cm}
% --- Summary ---
\section*{Summary}
Data Engineer with 1.8 years of experience building scalable data pipelines and backend systems. Skilled in Python, SQL, Airflow, AWS, GCP, and Snowflake, with proven success in automating deployments and cutting manual effort. Strong communicator, recognized with multiple awards for innovation, quality, and high-impact delivery.
\section*{Skills}
\begin{itemize}
    \item Programming: Python, SQL, Java, C/C++
    \item Data Engineering: Airflow, UC4, Snowflake
    \item Frameworks: Django, Streamlit
    \item Databases: MySQL, PostgreSQL
    \item Cloud \& DevOps: AWS, GCP, Git, Docker, Kubernetes
\end{itemize}

% --- Experience ---
\section*{Experience}
\textbf{Analyst (Data Engineering role)} \hfill Factspan Analytics, Bangalore \hfill Jan 2024 – Present\vspace{0.2cm}
\hrule
\vspace{0.2cm}
\begin{itemize}
    \item Designed and maintained scalable \textbf{ETL pipelines} for a \textbf{global entertainment leader}, using \textbf{Python, Airflow, UC4, AWS, and Snowflake}, to process terabytes of real-time data from diverse sources.
    \item \textbf{Migrated legacy data warehouses to Snowflake}, boosting query performance and scalability.
    \item \textbf{Developed automated data quality checks and development workflows}, reducing manual effort by 50\%.
    \item Leveraged internal enterprise data platform architecture to orchestrate deployments, enable CI/CD workflows, and streamline data engineering operations.
    \item \textbf{Recognitions \& Awards:}
    \begin{itemize}
        \item \textit{Learning Champ} – for outstanding performance in training initiatives.
        \item \textit{Sweat the Details} – for driving leading innovations and delivering exceptional quality.
        \item \textit{Spot Award} – for critical contributions to a high-impact project.
    \end{itemize}
\end{itemize}

% --- Education ---
\section*{Education}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{National Institute of Technology, Calicut, India} \hfill 2021 -- 2023 \\
          Master of Technology (M.Tech), Computer Science and Engineering (Information Security)
    \item \textbf{Government Engineering College, Thrissur, Kerala, India} \hfill 2016 -- 2020 \\
          Bachelor of Technology (B.Tech), Computer Science and Engineering
\end{itemize}

\section*{Certifications}
\begin{itemize}[leftmargin=0.5cm]
    \item Snowflake SnowPro Core Certified
    \item Google Cloud Digital Leader Certified
\end{itemize}

% % --- Projects ---
% \section*{Publications}
% \textbf{Automated Expense Tracker} | Python, Notion API, Google Sheets  
% - Developed a system that syncs Notion expense data with Google Sheets, providing daily/weekly/monthly insights.  

% \textbf{Productivity Task Manager} | React.js, Django  
% - Built a task manager with AI-based reminders to improve productivity tracking.  

\section*{Publications}
\begin{itemize}[leftmargin=0.5cm]
    \item Shyam Mohan V M, Krishnendhu S P, Prabu Mohandas. \textit{“Real-Time Traffic Signal Prediction and Control using Deep Q-Network”}, 2023 International Conference on Computer, Electronics \& Electrical Engineering \& their Applications (IC2E3), 2023.
\end{itemize}
\end{document}